Synpotic Soil Characterization

### 2024-11-11 3-reports/manuscript_figures.Rmd
manuscript figures

```{r analytesx-2, fig.height = 4, fig.width = 8, eval=FALSE}
data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = transect), alpha = 0.4)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
  scale_fill_manual(values = pal_transect)+
  theme(legend.position = "none")

@@

  ##  ggplot(data,
  ##         aes(x = transect,
  ##             y = value
  ##             #shape = horizon,
  ##             #alpha = horizon
  ##         )) +
  ##    # plot points
  ##    geom_point(aes(group = site,
  ##                   color = site),
  ##               size = 2.5, stroke = 1,
  ##               position = position_dodge(width = 0.4))+
  ##    # plot HSD letters
  ##    geom_text(data = lme_for_graphs, aes(y = y, label = groups), size = 5)+
  ##    scale_alpha_manual(values = c(1, 0.3))+
  ##    scale_color_manual(breaks = c("CRC", "PTR", "OWC", "GCW", "MSM", "GWI"), values = c('#ED6e85', '#7f4420', '#ffc115', '#90BE6D', '#03045E', '#00B4D8'))+
  ##    facet_wrap(~region, 
  ##               labeller = as_labeller(c("CB" = "Chesapeake Bay", "WLE" = "Lake Erie")))+
  ##    theme_kp()+
  ##    labs(x = "",
  ##        # y = YLAB,
  ##        # title = TITLE,
  ##        # subtitle = SUBTITLE,
  ##         shape = "Site",
  ##         alpha = "Horizon",
  ##         color = "Site")+
  ##    theme(legend.position = "right", legend.box = "vertical")+
  ##    NULL

@@

    geom_violin(aes(fill = transect), alpha = 0.4)+
    geom_jitter(width = 0.1)+
    geom_text(data = lme_for_graphs, aes(y = y, label = groups), size = 5)+
    labs(x = "",
         y = "Extractable P, μg/g")+
    facet_wrap(~region)+
    scale_fill_manual(values = pal_transect)+
    labs(x = "",
         y = YLAB,
         title = TITLE,
         subtitle = SUBTITLE,
         shape = "Site",
         alpha = "Horizon",
         color = "Site")+
    theme(legend.position = "none")+
    NULL

@@

cowplot::plot_grid(gg_tc, gg_fe, ncol = 1)

>>>>

```{r analytesx-2, fig.height = 4, fig.width = 8, eval=FALSE}
data_combined_wide %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc"))) %>% 
  ggplot(aes(x = transect, y = Fe))+
  geom_violin(aes(fill = region), alpha = 0.6)+
  geom_jitter(width = 0.1)+
  labs(x = "",
       y = "Extractable Fe, μg/g")+
  facet_wrap(~region)+
#  scale_fill_manual(values = c("darkblue", "red"))+
  scale_fill_manual(values = pnw_palette("Bay", 2))+
  theme(legend.position = "none")

@@

@@

    geom_violin(aes(fill = region), alpha = 0.4)+
    geom_jitter(width = 0.1)+
    geom_text(data = lme_for_graphs, aes(y = y, label = groups), size = 5)+
    labs(x = "",
         y = "Extractable P, μg/g")+
    facet_wrap(~region)+
    scale_fill_manual(values = pnw_palette("Bay", 2))+
    labs(x = "",
         y = YLAB,
         title = TITLE,
         subtitle = SUBTITLE,
         shape = "Site",
         alpha = "Horizon",
         color = "Site")+
    theme(legend.position = "none")+
    NULL

@@

cowplot::plot_grid(gg_fe, gg_p, ncol = 1)
